Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-03-19 review.qmd
Adding biblio
Adding contents of review_files folder.Perhaps ignore?

---
title: "Measuring contrast processing in the visual system using SSVEP (and VEP?)"
format: html
---

@@

*4: Clinical (Porciatti / Tsai/ Marmite/ Amblyopia / PD?)*

*5: Future directions (decoding in frequency domain?, animals? BCI?)*

>>>>

---
title: "Measuring contrast processing in the visual system using SSVEP (and VEP?)"
format: html
bibliography: WadeBaker_Review.bib
---

@@

*4: Clinical (Porciatti / Tsai/ Marmite/ Amblyopia / PD?)*
[@porciatti_lack_2000][@tsai_contrast_2011]
*5: Future directions (decoding in frequency domain?, animals? BCI?)*
